Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-08 paper.tex
a note about speedups in tex
added poster, modified algo

\begin{algorithm}[t]
    \KwIn{Temporal discretization $t^n = t_0 + n \Delta t, \, n = 1,2,\ldots,N$}
    \KwIn{Coarse scheme $g_{\Delta t}$}
    \KwIn{Finer scheme $g_{\textnormal{fine}}$}
    Compute $u_1^{n+1} = g_{\Delta t}(t^n, u^n)$\;
    Compute the corrections $\delta g^n(u_1^n) = g_{\textnormal{fine}}(t^n,
    u^n) - g_{\Delta t}(t^n, u^n)$ in parallel\;
    Add the prediction and correction terms as $u_2^{n+1} = g_{\Delta
    t}(t^n, u_2^n) + \delta g^n(u_1^n)$\;
    Repeat steps 2 and 3, incrementing the iteration label and using $u_{k+1}^0
    = u^0$ as the initial condition\
    }
 \caption{Parareal}
 \label{alg:parareal}
\end{algorithm}

@@

\subsection{Comparison to C++ Implementations}

>>>>

\begin{algorithm}[t]
    \KwIn{Temporal discretization $t^n = t_0 + n \Delta t, \, n = 1,2,\ldots,N$}
    \KwIn{Coarse scheme $g_{\Delta t}$}
    \KwIn{Finer scheme $g_{\textnormal{fine}}$}
    Compute $u_1^{n+1} = g_{\Delta t}(t^n, u^n)$\;
    Compute the corrections $\delta g^n(u_1^n) = g_{\textnormal{fine}}(t^n,
    u^n) - g_{\Delta t}(t^n, u^n)$ in parallel\;
    Add the prediction and correction terms as $u_2^{n+1} = g_{\Delta
    t}(t^n, u_2^n) + \delta g^n(u_1^n)$\;
    Repeat steps 2 and 3, incrementing the iteration label and using $u_{k+1}^0
    = u^0$ as the initial condition\
 \caption{Parareal}
 \label{alg:parareal}
\end{algorithm}

@@

\subsection{Comparison to C++ Implementations}
	The numpy environment combined with the required structure of MPI required certain type/data structure conversions which will take time.not not cunot cu
